Examples for Paper

### 2024-06-04 ExPro.Rmd
new file

\documentclass{article}

\begin{document}

@@

<<>>=
devtools::load_all()

# require(devtools)
devtools::install_github("filippogambarota/criticalvalue")

@

@@

<<>>=
library(psych)
library(psychTools)

data("holzinger.swineford")
Holz <- holzinger.swineford
@

@@

<<>>=
cc<-cor.test(Holz$t01_visperc, Holz$t02_cubes)
critical(cc)
critical.htest(cc)
@

In this first example we show how to calculate the critical value for a correlation test. We correlated two cognitive measures: visual perception and the cubes sub-test. It can be done by using firstly the 'cor.test' function and then putting the newly created object into the 'critical' function. The output will add, underneath the usual output of the 'cor.test' function, the absolute critical value (|rc|). The number represents the smallest significant effect. The same output can be obtained with the function 'critical.htest'.

@@

<<>>=
tt <- t.test(Holz$t01_visperc [ Holz$female == 1], Holz$t01_visperc [ Holz$female == 2])
critical(tt)
critical.htest(tt)
@

@@

<<>>=
ll <- lm( t01_visperc ~ ageyr , data = Holz)
summary(critical(ll))
@

@@

@@

<<>>=
n <- 1200
critical_t2s(n1 = n , n2 = n , hypothesis = "less")
@

@@

Critical t value from sample size for a paired t-test

<<>>=
n <- 15
critical_t2sp(n = n , hypothesis = "less")
@

@@

<<>>=
n <- 60
critical_cor(n = n, hypothesis = "two.sided", test = "z")
@

@@

<<>>=
n <- 170
critical_coef(seb = .1, n = n, p = .01, conf.level = .95, hypothesis = "less")
@

@@

\end{document}

>>>>

---
title: "Examples for Paper"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

@@

```{r load}
devtools::load_all()

# require(devtools)
#devtools::install_github("filippogambarota/criticalvalue")

```

## Examples on real data

@@

```{r open data}
library(psych)
library(psychTools)

data("holzinger.swineford")
Holz <- holzinger.swineford
```

@@

```{r correlation}
cc<-cor.test(Holz$t01_visperc, Holz$t02_cubes)
critical(cc)
critical.htest(cc)
```

In this first example we show how to calculate the critical value for a correlation test. We correlated two cognitive measures: visual perception and the cubes sub-test. It can be done by using firstly the 'cor.test' function and then putting the newly created object into the 'critical' function. The output will add, underneath the usual output of the 'cor.test' function, the absolute critical value (rc). The number represents the smallest significant effect. The same output can be obtained with the function 'critical.htest'.

@@

```{r}
tt <- t.test(Holz$t01_visperc [ Holz$female == 1], Holz$t01_visperc [ Holz$female == 2])
critical(tt)
critical.htest(tt)
```

@@

```{r}
ll <- lm( t01_visperc ~ ageyr , data = Holz)
summary(critical(ll))
```

@@

## Examples with sample size

@@

```{r t from n, echo=FALSE}
n <- 1200
critical_t2s(n1 = n , n2 = n , hypothesis = "less")
```

@@

Critical t value from sample size for a paired t-test.

```{r}
n <- 15
critical_t2sp(n = n , hypothesis = "less")
```

@@

```{r}
n <- 60
critical_cor(n = n, hypothesis = "two.sided", test = "z")
```

@@

```{r}
n <- 170
critical_coef(seb = .1, n = n, p = .01, conf.level = .95, hypothesis = "less")
```

@@
